Ordnung ist das halbe Leben -- Establishing Totally Ordered HTN Planning Problems is Half the Job (to Getting them Solved More Efficiently)

### 2022-11-28 paper/paper-mainfile.tex
Remove all grounded problem eval on lifted planners

\todo{Most notably, note that TO problems allow for other visited list
	configurations than PO problems. So we should also use a TO
	configuration there (this is however not reported)}

@@

@@

\begin{table}
	\centering
	\caption{Coverage achieved, using Complex Inference on Grounded Problems}
	\label{table:GroundedComplexCoverage}.
	\scalebox{0.7} {

\begin{tabular}{lccccccl} 
	\toprule 
	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} & HyperTensioN & Lilotane \\ 
	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
	&PO & TO &PO & TO  \\ 
	\midrule 
	Barman-BDI & 5.0 & \textbf{13.0} & 4.0 & \textbf{11.0}  \\ 
	Monroe Fully Observ.$^{5}$ & \textbf{25.0} & \textbf{25.0} & \textbf{22.0} & \textbf{22.0}  \\ 
	Monroe Part. Observ. & \textbf{14.0} & 13.0 & \textbf{14.0} & \textbf{14.0}  \\ 
	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{15.0} & \textbf{15.0}  \\ 
	Rover & 10.0 & \textbf{18.0} & 4.0 & \textbf{17.0}  \\ 
	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}  \\ 
	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}  \\ 
	Woodworking$^{1}$ & 13.0 & \textbf{20.0} & 12.0 & \textbf{19.0}  \\

@@

\begin{table}
	\centering
	\caption{IPC score achieved, using Complex Inference on Grounded Problems}
	\label{table:GroundedComplexIPC}.
	\scalebox{0.7} { 
\begin{tabular}{lccccccl} 
			\toprule 
		& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} & HyperTensioN & Lilotane \\ 
		\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
	&PO & TO  &PO & TO  \\ 
	\midrule 
	Barman-BDI & 0.09 & \textbf{0.34} & 0.06 & \textbf{0.34}  \\

@@

>>>>

%\todo{Most notably, note that TO problems allow for other visited list	configurations than PO problems. So we should also use a TO configuration there (this is however not reported)}

@@

The best results for Simple Inference on Grounded problems, as in Table~\ref{table:GroundedSimpleCoverage} and ~\ref{table:GroundedSimpleIPC},
achieve lower coverage but higher IPC score than Complex Inference on Grounded problems, as seen in Table~\ref{table:GroundedComplexCoverage} and ~\ref{table:GroundedComplexIPC}. This is due to complex inference taking a much greater ~98 seconds on average, where simple inference takes ~3 seconds on average. However, the slightly higher coverage does make it appear the complex inference pays off with \enquote{better} linearized domains. E.g.\ using complex inference consistently makes 7 problems solvable, whereas using simple inference, or no pre-processing, only solves for 5.

@@

\begin{table}
	\centering
	\caption{Coverage achieved, using Complex Inference on Grounded Problems}
	\label{table:GroundedComplexCoverage}.
	\scalebox{0.8} {

\begin{tabular}{lccccccl} 
	\toprule 
	&  \multicolumn{2}{c}{RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
	\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
	&PO & TO &PO & TO  \\ 
	\midrule 
	Barman-BDI & 5.0 & \textbf{13.0} & 4.0 & \textbf{11.0}  \\ 
	Monroe Fully Observ.$^{5}$ & \textbf{25.0} & \textbf{25.0} & \textbf{22.0} & \textbf{22.0}  \\ 
	Monroe Part. Observ. & \textbf{14.0} & 13.0 & \textbf{14.0} & \textbf{14.0}  \\ 
	Norm. coverage & 8.44 & \textbf{10.07} & 8.02 & \textbf{9.59}  \\ 
	PCP$^{17}$ & \textbf{14.0} & \textbf{14.0} & \textbf{15.0} & \textbf{15.0}  \\ 
	Rover & 10.0 & \textbf{18.0} & 4.0 & \textbf{17.0}  \\ 
	Satellite & 24.0 & \textbf{25.0} & \textbf{25.0} & \textbf{25.0}  \\ 
	Transport & 12.0 & \textbf{28.0} & 13.0 & \textbf{14.0}  \\ 
	UM-Translog$^{1}$ & \textbf{22.0} & \textbf{22.0} & \textbf{22.0} & \textbf{22.0}  \\ 
	Woodworking$^{1}$ & 13.0 & \textbf{20.0} & 12.0 & \textbf{19.0}  \\

@@

\begin{table}
	\centering
	\caption{IPC score achieved, using Complex Inference on Grounded Problems}
	\label{table:GroundedComplexIPC}.
	\scalebox{0.8} { 
\begin{tabular}{lccccccl} 
			\toprule 
		& \multicolumn{2}{c}{ RC Add} & \multicolumn{2}{c}{ RC FF} \\ %& HyperTensioN & Lilotane \\ 
		\cmidrule(lr){2-3} \cmidrule(lr){4-5}  
	&PO & TO  &PO & TO  \\ 
	\midrule 
	Barman-BDI & 0.09 & \textbf{0.34} & 0.06 & \textbf{0.34}  \\

@@

\begin{table} 
	\centering
	\caption{These results are from using Simple Inference. Table shows the average number of methods per domain with more than 1 sub-task, the average number of those methods that needed cycle-breaking, and the percentage of successfully linearized methods.}
	\label{table:SimpleLinearizable} 
		\scalebox{0.75} { 
	\begin{tabular}{lcccl} 
		\toprule 
		&$>$ 1 subtasks & Cycle-breaking & Percentage &  \\ 
		\midrule
Barman-BDI & 4870.0 & 3717.1 & 28.6  \\ 
Monroe & 12127.3 & 3447.8 & 72.4  \\ 
Monroe Fully Observ. & 49450.6 & 15813.0 & 68.0  \\ 
Monroe Part. Observ. & 49470.9 & 15809.3 & 68.0  \\ 
PCP & 12.3 & 12.3 & 0.0  \\ 
Rover & 509.4 & 355.2 & 32.3  \\ 
Satellite & 70.6 & 36.1 & 50.9  \\ 
SmartPhone & 6.3 & 4.0 & 21.8  \\ 
Transport & 1144.9 & 1144.9 & 0.0  \\ 
UM-Translog & 1.5 & 1.5 & 0.0  \\ 
Woodworking & 1927.3 & 1927.3 & 0.0  \\ 
Zenotravel & 190.2 & 99.4 & 47.0  \\ 
		\bottomrule 
	\end{tabular} 
}
\end{table}

\begin{table} 
	\centering
	\caption{These results are the same as Table~\ref{table:SimpleLinearizable}, but from using Complex Inference.}
	\label{table:ComplexLinearizable} 
	\scalebox{0.75} { 
	\begin{tabular}{lcccl} 
		\toprule 
		&$>$ 1 subtasks & Cycle-breaking & Percentage &  \\ 
		\midrule
			Barman-BDI &  4870.0 & 1836.0 & 62.2  \\ 
			Monroe & 12127.3 & 216.9 & 98.2  \\ 
			Monroe Fully Observ. & 49450.6 & 1016.2 & 97.9  \\ 
			Monroe Part. Observ. & 49470.9 & 1010.0 & 98.0  \\ 
			PCP & 12.3 & 4.9 & 59.8  \\ 
			Rover & 509.4 & 134.8 & 72.4  \\ 
			Satellite & 70.6 & 10.7 & 77.9  \\ 
			SmartPhone & 6.3 & 0.9 & 77.4  \\ 
			Transport & 1144.9 & 0.0 & 100.0  \\ 
			UM-Translog & 1.5 & 0.4 & 87.9  \\ 
			Woodworking & 1927.3 & 476.0 & 85.5  \\
			Zenotravel & 190.2 & 16.4 & 91.6  \\ 
			\bottomrule 
		\end{tabular} 
		}
\end{table}
